Tight Generalization Bounds for Hard Parameter Sharing in High-dimensional Linear Regression

### 2020-10-14 arxiv/conclusions.tex
typos

This work proposed a formal study of a widely used hard paramaeter sharing approach in high-dimensional linear regression, where the sample size and feature dimension increase at a fixed ratio.
We provided tight generalization bounds that scale with dataset properties such as their sample sizes and covariate shifts.
Based on these bounds, we analyzed the impact of varying sample sizes and covariate shifts on the prediction loss of hard parameter sharing.
Our work rigorously explains several empirical phenomena such as sample efficiency and negative transfer related to these dataset properties.
We validated our results and conducted further studies on a real world classification task.

We describe several open questions for future work.
First, our bound in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic random matrices.
This requires studying the asymptotic distribution of the {singular values} of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}$, which is still an open problem in random matrix theory. The eigenvalue distribution of this matrix, which has been obtained in \citet{Fmatrix}, might be helpful towards resolving this problem.
%but its singular values will follow a different distribution since the matrix is not symmetric.
 %might require new techniques beyond the current ones in random matrix theory .%\HZ{to add}.
Second, it would be interesting to extend our results to classification problems.
Several recent work have made remarkable progress for logistic regression in the high-dimensional  setting, e.g. \cite{sur2019modern}.
An interesting question is to study logistic regression in a multiple-sample setting.

>>>>

This work proposed a formal study of a widely used hard paramaeter sharing approach in high-dimensional linear regression, where the sample size and feature dimension increase at a fixed ratio.
We provided tight generalization bounds that scale with dataset properties such as the sample sizes and covariate shifts.
Based on these bounds, we analyzed the impact of varying sample sizes and covariate shifts on the prediction loss of hard parameter sharing.
Our work rigorously explains several empirical phenomena such as sample efficiency and negative transfer related to these dataset properties.
We validated our results and conducted further studies on a real world classification task.

We describe several open questions for future work.
First, our bound in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic sample covariance matrices.
This requires studying the asymptotic singular values distribution of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}+\id$, which is still an open problem in random matrix theory.  
%FY: $+\id$ is very important and makes the problem very hard; otherwise the problem can be solved with current RMT methods.
The eigenvalue distribution of this matrix, which has been obtained in \citet{Fmatrix}, might be helpful towards resolving this problem.
%but its singular values will follow a different distribution since the matrix is not symmetric.
 %might require new techniques beyond the current ones in random matrix theory .%\HZ{to add}.
Second, it would be interesting to extend our results to classification problems.
Several recent work have made remarkable progress for logistic regression in the high-dimensional  setting, e.g. \citet{sur2019modern}.
An interesting question is to study logistic regression in a multiple-sample setting.

### 2020-10-14 arxiv/experiments.tex
typos

We demonstrate the accuracy of our results via some empirical results.
While our theory is asymptotic (with error terms that is negligible when $p$ is sufficiently large), we observe that they are accurate in a moderate dimension of $p = 200$.

\textbf{Sample efficiency.}
First, we study the setting of Example \ref{ex_same_cov}.
Figure \ref{fig_same_cov} shows the average prediction loss as we increase the number of samples per-task   from $400$ to $2000$.
In all the parameter settings, our results estimate the empirical losses accurately.
We also observe a trend where the average prediction loss increases as we increase $d$ from $0.1$ to $0.2$.
Our work explains the differences between these two settings since $d^2 = 0.1^2$ is always smaller than $\frac{\sigma^2 p}{n - p}$, but $d^2 = 0.2^2$ is not.
%Second, when $d = 0.1$, we have that $d^2 \le \frac{\sigma^2 p}{n - p}$ for all values of $n$, hence the average prediction loss of hard parameter sharing is always lower than STL.
Indeed, we observe a crossover point between hard parameter sharing and STL.
Finally, for $d = 0.2$, looking horizontally at the same prediction loss level, we find that hard parameter sharing requires fewer samples per-task than STL. %\FY{I do not quite understand this sentence about "3x fewer", because how much data needed depends on $d$ and the prediction loss level we are looking at. For example, at the cross point, this ratio is 1. }

@@

\textbf{Covariate shift.}
Finally, we show how varying covariate shift impacts hard parameter sharing in the setting of Example \ref{ex_covshift}. 
Figure \ref{fig_covariate} shows task two's prediction loss as we increase task one's sample size.
Recall that $\lambda$ measures the severity of covariate shifts---a larger $\lambda$ means more covariate shift.
Our estimates match the empirical losses accurately, and indeed we observe the dichotomy in Example \ref{ex_covshift}.
The noise variance $\sigma^2$ is $1/4$.
%Covariate shift: We set $\kappa = 1$ and $d = 0$.
%We set $\rho_2 = 4$ and vary $\rho_1$ from $5$ to $25$ for sample sizes.
%We use the scale parameter $\lambda = 1$ for the curve without covariate shift and $\lambda = 2$ for the curve with covariate shift (cf. Section \ref{sec_covshift}).

>>>>

We demonstrate the accuracy of our results via some empirical results.
While our theory is asymptotic (with error terms that are negligible when $p$ is sufficiently large), we observe that they are accurate in a moderate dimension of $p = 200$.

\textbf{Sample efficiency.}
First, we study the setting of Example \ref{ex_same_cov}.
Figure \ref{fig_same_cov} shows the average prediction loss as we increase the number of samples per-task   from $400$ to $2000$.
In all the parameter settings, our results estimate the empirical losses accurately.
We also observe a trend that the average prediction loss increases as we increase $d$ from $0.1$ to $0.2$.
Our work explains the differences between these two settings since $d^2 = 0.1^2$ is always smaller than $\frac{\sigma^2 p}{n - p}$, but $d^2 = 0.2^2$ is not.
%Second, when $d = 0.1$, we have that $d^2 \le \frac{\sigma^2 p}{n - p}$ for all values of $n$, hence the average prediction loss of hard parameter sharing is always lower than STL.
Indeed, we observe a crossover point between hard parameter sharing and STL.
Finally, for $d = 0.2$, looking horizontally at the same prediction loss level, we find that hard parameter sharing requires fewer samples per-task than STL. %\FY{I do not quite understand this sentence about "3x fewer", because how much data needed depends on $d$ and the prediction loss level we are looking at. For example, at the cross point, this ratio is 1. }

@@

\textbf{Covariate shift.}
Finally, we show how varying covariate shift impacts hard parameter sharing in the setting of Example \ref{ex_covshift}. 
Figure \ref{fig_covariate} shows task two's prediction loss as we increase task one's sample size.
Recall that $\lambda$ measures the severity of covariate shifts---a larger $\lambda$ means a larger covariate shift.
Our estimates match the empirical losses accurately, and indeed we observe the dichotomy in Example \ref{ex_covshift}.
The noise variance $\sigma^2$ is $1/4$.
%Covariate shift: We set $\kappa = 1$ and $d = 0$.
%We set $\rho_2 = 4$ and vary $\rho_1$ from $5$ to $25$ for sample sizes.
%We use the scale parameter $\lambda = 1$ for the curve without covariate shift and $\lambda = 2$ for the curve with covariate shift (cf. Section \ref{sec_covshift}).
